---
title: "Challenge 3"
author: "Dominik Haller"
---
```{r}
require(tidyverse)
require(GGally)
#As I could not get plot_ggpairs to work I have used an alternate package GGally to plot pairs plots

employee_attrition_tbl <- read_csv("~/GitHub/ss23-bdml-dohaller/code/dataset_employees.csv")
```
## Monthly Income
```{r}
employee_attrition_tbl %>% 
  select(Attrition, MonthlyIncome) %>% 
  ggpairs()
```
We can deduce that those that are leaving are more likely to be the ones with lower income as seen in the upper right plot.
Answer: C

## Compensation Features
```{r}
employee_attrition_tbl %>% 
  select(Attrition, PercentSalaryHike) %>% 
  ggpairs()
```
It is difficult to deduce anything from this plot. Answer: D

## Stock Options
```{r}
employee_attrition_tbl %>% 
  select(Attrition, StockOptionLevel) %>% 
  ggpairs()
```
It is difficult to deduce anything from this plot. Answer: D

## Survey Results
```{r}
employee_attrition_tbl %>% 
  select(Attrition, EnvironmentSatisfaction) %>% 
  ggpairs()
```
It is difficult to deduce anything from this plot. Although those with higher environment satisfaction may be more inclined to stay. Answer: A

## Work Life Balance
```{r}
employee_attrition_tbl %>% 
  select(Attrition, WorkLifeBalance) %>% 
  ggpairs()

```
It is difficult to deduce anything from this plot. Answer: D

## Performance Data
```{r}
employee_attrition_tbl %>% 
  select(Attrition, JobInvolvement) %>% 
  ggpairs()
```
It is difficult to deduce anything from this plot. Answer: D

## Overtime
```{r}
employee_attrition_tbl %>% 
  select(Attrition, OverTime) %>% 
  ggpairs()
```
It is difficult to deduce anything from this plot. Answer: D

## Training and Education
```{r}
employee_attrition_tbl %>% 
  select(Attrition, TrainingTimesLastYear) %>% 
  ggpairs()
```
It is difficult to deduce anything from this plot. Answer: D

## Time Based Features
```{r}
employee_attrition_tbl %>% 
  select(Attrition, YearsAtCompany) %>% 
  ggpairs()
```
Those with less years tend to leave or rather those with more years tend to stay. Answer: B

## Time Based Features
```{r}
employee_attrition_tbl %>% 
  select(Attrition, YearsSinceLastPromotion) %>% 
  ggpairs()
```
It is difficult to deduce anything from this plot. Answer: D